Rethinking Felony Disenfranchisement: The Case of New York City and Miami

### 2019-04-25 markdown/paper.Rmd
figure out figures

---
title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami"
author: "Kevin Morris"
date: "April 22, 2019"
output: pdf_document
bibliography: "test.bib"
link-citations: yes
---
<!-- --- -->
<!-- title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami" -->

@@

<!-- output: rticles::asa_article -->
<!-- --- -->
```{r setup, echo = F, message = F}
knitr::opts_knit$set(root.dir = "..")
library(scales)
library(ggplot2)
library(extrafont)
```
"There is no Negro problem. There is no Southern problem. There is no Northern problem. There is only an American problem"

@@

#Maps
![\label{fig:citymap}Individuals Incarcerated in 2017 Who Voted Between 2007 and 2016](../output/citywide_map.png)

As we can see in Figure \ref{fig:citymap}, these are not distributed evenly throughout the city.

>>>>

---
title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami"
author: "Kevin Morris"
date: "April 22, 2019"
output:
  pdf_document:
    fig_caption: yes
bibliography: "test.bib"
link-citations: yes
---
<!-- --- -->
<!-- title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami" -->

@@

<!-- output: rticles::asa_article -->
<!-- --- -->
```{r setup, echo = F, message = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf"
                     )
library(scales)
library(ggplot2)
library(extrafont)
```
"There is no Negro problem. There is no Southern problem. There is no Northern problem. There is only an American problem"

@@

#Maps
```{r figs, echo = FALSE, fig.width = 5, fig.height = 5, fig.cap = "\\label{fig:citymap}Individuals Incarcerated in 2017 Who Voted Between 2007 and 2016"}
j <- readRDS("./output/city_map.RDS")
j
```

As we can see in Figure \ref{fig:citymap}, all these other observations
